### 2016-12-29 paper/paris17/paper.tex
add figures

\documentclass{paris17}
\usepackage{amsmath}
\begin{document}

@@

Explicit finite difference modeling is constrained by figuring  out a sampling in time and space that results in stable propagation and does not create dispersive events.  For stability the Courant-Friedrichs-Lewy condition \cite[]{courant1967partial} must be met.  Stability is a function of limiting what percentage of a grid cell energy can move in one time step. Stability is therefore a function of the maximum velocity $v_{max}$, the minimum spatial sampling $d_{min}$, and the time step $dt$. For stability,

\begin{equation}
v_{max}\frac{dt}{d_{min}} < .5 \label{eq:stability}.
\end{equation}

The stability condition pushes one to use larger spatial sampling (faster, but less resolution) and/or finer time sampling (more expensive).  Dispersion, on the other hand, is a function of the minimum velocity $v_{min}$, the maximum frequency $f_{max}$, and the maximum spaital sampling $d_{max}$.   To avoid grid dispersion we need to  sample a given frequency with a minimum number of points.  There isn't a consensus on the minimum number
of points. For the purpose of this paper I will require  3.2  points therefore,

\begin{equation}
\frac{v_{min} }{f_{max}d_{max}} > 3.2 \label{eq:dispersion}.
\end{equation}

@@

From observation we know that the earth attenuates acoustic signals.  Attenuation varies as a function of frequency and earth materials. The first approximation I am going to use is the concept of the constant Q model introduced by \cite{Kjartansson.sep.23}.  Q is defined as

\begin{equation}
Q=2 \pi \left( \frac{E}{\partial E}\right),
\end{equation}

where $\frac{E}{\partial E}$ is the fraction of energy lost per cycle. The larger the $Q$ value, the less energy loss per cycles.  The constant Q assumption assumes that energy dies out is a function of the number of wavelengths traveled through a medium. The higher the frequency, the faster the energy is attenuated.

@@

Firstly, we fully utilize the different hierarchical memory of the GPU. We keep a set of constant variables such as the derivative coefficients in the constant memory and the read-only cache. As the 64KB first-level cache can be configured as different combinations between L1 cache and shared memory, we configure it dynamically based on different computing scenarios. For the stencil computation, we configure the first-level cache by setting the sizes of shared memory and L1 cache to be 48 KB and 16 KB, respectively, which achieves a high computation performance based on P. Micikevicius’ 3D stencil design. For others, we prefer to configure the first-level cache as L1 cache if we don't use memory explicitly.

@@

@@

Table xxx shows the performance speedup on using different number of GPUs. Through combining the GPU optimization schemes above, the GPU design amoung four K40 cards improve the performance by upto xxx times over xxx cores. Note that the CPU design is also tuned by using multi-threading and vectorizations.

@@

\section{Examples (Optional)}

This is the first sentence of the example section.

\section{Results (Optional)}

This is the first sentence of the result section.

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=0.6\textwidth]{....eps}
%   \caption{...}
% \end{figure}

@@

\section{Acknowledgements (Optional)}

This is the first sentence of the acknowledgements.

>>>>

\documentclass{paris17}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{floatrow}
% Table float box with bottom caption, box width adjusted to content
\newfloatcommand{capbtabbox}{table}[][\FBwidth]
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}

\begin{document}

@@

Explicit finite difference modeling is constrained by figuring  out a sampling in time and space that results in stable propagation and does not create dispersive events.  For stability the Courant-Friedrichs-Lewy condition \cite[]{courant1967partial} must be met.  Stability is a function of limiting what percentage of a grid cell energy can move in one time step. Stability is therefore a function of the maximum velocity $v_{max}$, the minimum spatial sampling $d_{min}$, and the time step $dt$. For stability, we have $v_{max}\frac{dt}{d_{min}} < .5$.

The stability condition pushes one to use larger spatial sampling (faster, but less resolution) and/or finer time sampling (more expensive).  Dispersion, on the other hand, is a function of the minimum velocity $v_{min}$, the maximum frequency $f_{max}$, and the maximum spaital sampling $d_{max}$.   To avoid grid dispersion we need to  sample a given frequency with a minimum number of points.  There isn't a consensus on the minimum number
of points. For the purpose of this paper I will require  3.2  points therefore, we have $\frac{v_{min} }{f_{max}d_{max}} > 3.2 \label{eq:dispersion}$.

@@

From observation we know that the earth attenuates acoustic signals.  Attenuation varies as a function of frequency and earth materials. The first approximation I am going to use is the concept of the constant Q model introduced by \cite{Kjartansson.sep.23}.  Q is defined as $Q=2 \pi \left( \frac{E}{\partial E}\right)$, where $\frac{E}{\partial E}$ is the fraction of energy lost per cycle. The larger the $Q$ value, the less energy loss per cycles.  The constant Q assumption assumes that energy dies out is a function of the number of wavelengths traveled through a medium. The higher the frequency, the faster the energy is attenuated.

@@

Firstly, we fully utilize the different hierarchical memory of the GPU. We keep a set of constant variables such as the derivative coefficients in the constant memory and the read-only cache. As the 64KB first-level cache can be configured as different combinations between L1 cache and shared memory, we configure it dynamically based on different computing scenarios. For the stencil computation, we configure the first-level cache by setting the sizes of shared memory and L1 cache to be 48 KB and 16 KB, respectively, which achieves a high computation performance based on P. Micikevicius’ 3D stencil design. For others, we prefer to configure the first-level cache as L1 cache if we don't use shared memory explicitly.

Secondly, we carefully tune the number of registers per thread to maximize the occupancy of GPUs. Since the access pattern of GPU global memory in the stencil kernel is irregular, the more threads are busy, the less latencies it is for memory access. However, as the number of registers is limited in a streaming multiprocessor (SM), increasing the number of registers per threads will decrease the number of active warps. So it is important to have a strategy to balance them. We first remove the intermediate variables to reduce the number of registers per threads. Then we dynamically tracking the performance by adjusting the block size and the \emph{maxrregcount} compiler option.

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[height=1.3in]{./fig/domain-decompose.pdf}
        \caption{Domain decomposition}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[height=1.3in]{./fig/inner-outer.pdf}
        \caption{Task decomposition}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[height=1.1in]{./fig/overlap.pdf}
        \caption{Comp. \& Comm. overlapping}
    \end{subfigure}
    \caption{Computation and communication overlapping over multiple GPUs.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[height=1.3in]{./fig/std.pdf}
        \caption{Wavefield without attenuation}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[height=1.3in]{./fig/q20.pdf}
        \caption{Wavefield with attenuation}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[height=1.3in]{./fig/spec.eps}
        \caption{Spectrum of the wavefields}
    \end{subfigure}
    \caption{Wavefields with and without attenuation.}
\end{figure}

@@

Table xxx shows the performance speedup on using different number of GPUs. Through combining the GPU optimization schemes above, the GPU design amoung four K40 cards improve the performance by upto xxx times over xxx cores. Note that the CPU design is also tuned by using multi-threading and vectorizations.
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[height=1.5in]{./fig/speedup.eps}
%        \caption{Wavefield without attenuation}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[height=1.5in]{./fig/speedup_q.eps}
%        \caption{Wavefield with attenuation}
    \end{subfigure}
    \caption{Wavefields with and without attenuation.}
\end{figure}

@@

@@
